COVID19 - Forecast and predictions using a time dependent SEIR model for the Veneto Region

### 2020-04-07 draft_analysis_Italy_html.Rmd
Add home page, navigation and theme

```{r}
names(dat_csv[,-c(1:2,13)])

@@

```{r}
myDateTimeStr1 <- dat_csv$data
myPOSIXct1 <- as.POSIXct(myDateTimeStr1, format="%Y-%m-%d %H:%M:%S")
days_dy<-as.Date(myPOSIXct1)
dat_csv_dy<-xts(dat_csv[,-c(1:2,12:13)], order.by = days_dy, frequency = 7)
```

```{r}
p <- dygraph(dat_csv_dy,main=paste("Italy",sep =""),xlab="Day",height=400,width=800) 
p
```

### The S(E)IR model (to be revised)

With the aim of predicting the future number of COVID19 cases on the
basis of the actual data, we used a SEIR model applied to the COVID19
epidemic to Italy

>>>>

```{r}
names(dat_csv[,-c(1:2,14:16)])

@@

```{r}
myDateTimeStr1 <- paste(substr(dat_csv$data,1,10),substr(dat_csv$data,12,19))
myPOSIXct1 <- as.POSIXct(myDateTimeStr1, format="%Y-%m-%d %H:%M:%S")
days_dy<-as.Date(myPOSIXct1)
dat_csv_dy<-xts(dat_csv[,-c(1:2,14:16)], order.by = days_dy, frequency = 7)
```

```{r}
p <- dygraph(dat_csv_dy,main=paste("Italy",sep =""),xlab="Day",height=400,width=800) 
p
```
The time series of COVID-19 in the Italy.

```{r}
plot(days_dy[-1],diff(dat_csv$totale_casi), ylab="New cases",xlab="Date",type="l")
```
### The S(E)IR model (to be revised)

With the aim of predicting the future number of COVID19 cases on the
basis of the actual data, we used a SEIR model applied to the COVID19
epidemic to the Italy.

### 2020-04-07 draft_analysis_Veneto_new.Rmd
Add home page, navigation and theme

$$\sigma_{\beta_N}^2 =-2\log(\mu_{\beta_{LogN}})+\log(\mu_{\beta_{LogN}}^2+\sigma_{\beta_{LogN}}^2)$$
This transformation permits us to perform an inference based on the classical regression model for the predict forward of the future values of $ \beta_{LogN}(t) $ with a direct transformation.

@@

```{r  intensive care numbers, echo=TRUE}
fit_int_care<-glm(cbind(terapia_intensiva,totale_positivi-terapia_intensiva)~t,family=binomial,data=dat_csv)

forecast=14
# add 'fit', 'lwr', and 'upr' columns to dataframe (generated by predict)
pre<-predict(fit_int_care,type='response',newdata=data.frame(t=1:(days+forecast)),se.fit=TRUE)
date<-seq(as.Date("2020-02-24"),as.Date("2020-02-24")+forecast-1+dim(dat_csv)[1],1)
plot(date,pre$fit,type="l",main="Proportion of admitted COVID 19 in intensive care",ylim=range(dat_csv$terapia_intensiva/dat_csv$totale_positivi))
points(date[1:days],dat_csv$terapia_intensiva/dat_csv$totale_positivi)
lines(date,pre$fit+1.96*pre$se.fit,col=3,lty=2)
lines(date,pre$fit-1.96*pre$se.fit,col=3,lty=2)
legend("topright",c("fitted","95% Confidence Interval"),lty=1:2,col=c(1,3))

>>>>

$$\sigma_{\beta_N}^2 =-2\log(\mu_{\beta_{LogN}})+\log(\mu_{\beta_{LogN}}^2+\sigma_{\beta_{LogN}}^2)$$
This transformation permits us to perform an inference based on the classical regression model for the predict forward of the future values of $\beta_{LogN}(t)$ with a direct transformation.

@@

```{r  intensive care numbers, echo=TRUE}
fit_int_care<-glm(cbind(terapia_intensiva,totale_positivi-terapia_intensiva)~t+I(t^2),family=binomial,data=dat_csv[])

forecast=14
# add 'fit', 'lwr', and 'upr' columns to dataframe (generated by predict)
pre<-predict(fit_int_care,type='response',newdata=data.frame(t=1:(days+forecast)),se.fit=TRUE)
date<-seq(as.Date("2020-02-24"),as.Date("2020-02-24")+forecast-1+dim(dat_csv)[1],1)
plot(date,pre$fit,type="l",main="Proportion of admitted COVID 19 in intensive care",ylim=range(c(dat_csv$terapia_intensiva/dat_csv$totale_positivi,pre$fit)))
points(date[1:days],dat_csv$terapia_intensiva/dat_csv$totale_positivi)
lines(date,pre$fit+1.96*pre$se.fit,col=3,lty=2)
lines(date,pre$fit-1.96*pre$se.fit,col=3,lty=2)
legend("topright",c("fitted","95% Confidence Interval"),lty=1:2,col=c(1,3))
